Informing IPCC accounting of forest carbon using the global forest carbon database (ForC v4.0)

### 2023-05-12 doc/manuscript/ESSDmanuscript.Rmd
delete mismatches section
Not critical, and I don't feel like writing this! :-)

#Cited sections (listed here because these can change)
section_C_pools = 2.1 
section_land_use_categories = 2.2
section_new_variables = 3.2
section_C_variable_mapping = "4.1.1"
section_land_use_mapping = "4.1.2"
section_database_needs = "6.1"
section_new_data_needs = "6.2"
section_data_reporting_needs = "6.3" 
section_mismatches = 6.4

@@

Based on our experience contributing forest C data to EFDB via ForC, we make several recommendations as to how scientists can improve forest C records in EFDB through database work (section `r section_database_needs`), new data collection and analysis (section `r section_new_data_needs`), and reporting (section `r section_data_reporting_needs`).
We also highlight notable mismatches between IPCC accounting methods and forest C mensuration (section `r section_mismatches`).

@@

We recommend that, in order to make research valuable to C accounting under IPCC guidelines, researchers calculate and report results according to IPCC standards (Table `r table_recommendations`).
It is particularly noteworthy that simple decisions on the presentation of results will determine whether the records meet the criteria for inclusion in EFDB.
Some examples are as follows:
(1) presenting data only in a figure makes them ineligible for inclusion in EFDB, whereas presentation in a table or supplementary data file allows inclusion;
(2) direct presentation of all relevant variables allows inclusion, whereas presenting only components of variables of interest (e.g., parsing litter into fine woody debris, OL, OF, and OH layers) or requiring simple mathematical operations to obtain a variable of interest (e.g., *delta.agb* = *ANPP_woody* - *woody.mortality.agb*) disqualifies records from inclusion;
(3) matching IPCC-defined thresholds for defining C pools (Table `r table_pools`), which may vary by country, can make the data far more relevant for IPCC accounting (e.g., using a 10 cm cutoff between dead wood and litter, presenting soil C to a depth of 30 cm).
It should also be emphasized that reporting of 95% confidence intervals (or other metrics of error), when applicable, is highly desirable and makes the data more relevant to IPCC. Reports which had the most successful data transfers used EFDB variables and had clear tables showing their results.

@@

## Mismatches between IPCC accounting methods and forest C mensuration

Remote sensing biomass estimates include standing dead wood [@duncanson_aboveground_2021].

IPCC accounting methods cannot leverage eddy-covariance measurements, which are widely seen as the best available method for quantifying ecosystem-atmosphere gas exchange.

>>>>

#Cited sections (listed here because these can change)
section_C_pools = 2.1 
section_land_use_categories = 2.2
section_new_variables = 3.2
section_C_variable_mapping = "4.1.1"
section_land_use_mapping = "4.1.2"
section_database_needs = "6.1"
section_new_data_needs = "6.2"
section_data_reporting_needs = "6.3"

@@

Based on our experience contributing forest C data to EFDB via ForC, we make several recommendations as to how scientists can improve forest C records in EFDB through database work (section `r section_database_needs`), new data collection and analysis (section `r section_new_data_needs`), and reporting (section `r section_data_reporting_needs`).

@@

We recommend that, in order to make research valuable to C accounting under IPCC guidelines, researchers calculate and report results according to IPCC standards (Table `r table_recommendations`).
It is particularly noteworthy that simple decisions on the presentation of results will determine whether the records meet the criteria for inclusion in EFDB.
Some examples are as follows:
(1) presenting data only in a figure makes them ineligible for inclusion in EFDB, whereas presentation in a table or supplementary data file allows inclusion;
(2) direct presentation of all relevant variables allows inclusion, whereas presenting only components of variables of interest (e.g., parsing litter into fine woody debris, OL, OF, and OH layers) or requiring simple mathematical operations to obtain a variable of interest (e.g., *delta.agb* = *ANPP_woody* - *woody.mortality.agb*) disqualifies records from inclusion;
(3) matching IPCC-defined thresholds for defining C pools (Table `r table_pools`), which may vary by country, can make the data far more relevant for IPCC accounting (e.g., using a 10 cm cutoff between dead wood and litter, presenting soil C to a depth of 30 cm).
It should also be emphasized that reporting of 95% confidence intervals (or other metrics of error), when applicable, is highly desirable and makes the data more relevant to IPCC.

@@

### 2023-05-12 doc/manuscript/ESSDmanuscript.tex
delete mismatches section
Not critical, and I don't feel like writing this! :-)

Based on our experience contributing forest C data to EFDB via ForC, we
make several recommendations as to how scientists can improve forest C
records in EFDB through database work (section 6.1), new data collection
and analysis (section 6.2), and reporting (section 6.3). We also
highlight notable mismatches between IPCC accounting methods and forest
C mensuration (section 6.4).

@@

We recommend that, in order to make research valuable to C accounting
under IPCC guidelines, researchers calculate and report results
according to IPCC standards (Table 3). It is particularly noteworthy
that simple decisions on the presentation of results will determine
whether the records meet the criteria for inclusion in EFDB. Some
examples are as follows: (1) presenting data only in a figure makes them
ineligible for inclusion in EFDB, whereas presentation in a table or
supplementary data file allows inclusion; (2) direct presentation of all
relevant variables allows inclusion, whereas presenting only components
of variables of interest (e.g., parsing litter into fine woody debris,
OL, OF, and OH layers) or requiring simple mathematical operations to
obtain a variable of interest (e.g., \emph{delta.agb} =
\emph{ANPP\_woody} - \emph{woody.mortality.agb}) disqualifies records
from inclusion; (3) matching IPCC-defined thresholds for defining C
pools (Table 1), which may vary by country, can make the data far more
relevant for IPCC accounting (e.g., using a 10 cm cutoff between dead
wood and litter, presenting soil C to a depth of 30 cm). It should also
be emphasized that reporting of 95\% confidence intervals (or other
metrics of error), when applicable, is highly desirable and makes the
data more relevant to IPCC. Reports which had the most successful data
transfers used EFDB variables and had clear tables showing their
results.

@@

\subsection{Mismatches between IPCC accounting methods and forest C
mensuration}

Remote sensing biomass estimates include standing dead wood
\citep{duncanson_aboveground_2021}.

IPCC accounting methods cannot leverage eddy-covariance measurements,
which are widely seen as the best available method for quantifying
ecosystem-atmosphere gas exchange.

>>>>

Based on our experience contributing forest C data to EFDB via ForC, we
make several recommendations as to how scientists can improve forest C
records in EFDB through database work (section 6.1), new data collection
and analysis (section 6.2), and reporting (section 6.3).

@@

We recommend that, in order to make research valuable to C accounting
under IPCC guidelines, researchers calculate and report results
according to IPCC standards (Table 3). It is particularly noteworthy
that simple decisions on the presentation of results will determine
whether the records meet the criteria for inclusion in EFDB. Some
examples are as follows: (1) presenting data only in a figure makes them
ineligible for inclusion in EFDB, whereas presentation in a table or
supplementary data file allows inclusion; (2) direct presentation of all
relevant variables allows inclusion, whereas presenting only components
of variables of interest (e.g., parsing litter into fine woody debris,
OL, OF, and OH layers) or requiring simple mathematical operations to
obtain a variable of interest (e.g., \emph{delta.agb} =
\emph{ANPP\_woody} - \emph{woody.mortality.agb}) disqualifies records
from inclusion; (3) matching IPCC-defined thresholds for defining C
pools (Table 1), which may vary by country, can make the data far more
relevant for IPCC accounting (e.g., using a 10 cm cutoff between dead
wood and litter, presenting soil C to a depth of 30 cm). It should also
be emphasized that reporting of 95\% confidence intervals (or other
metrics of error), when applicable, is highly desirable and makes the
data more relevant to IPCC.

@@
